E Coli Project Paper Incredibly Rough Draft

### 2013-10-16 paper/paper.tex
wrote more paper Tested everything on node31.

\subsection{Triangular Shapes}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-400-400-400-1500}
  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-500-300-500-1500}
  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-480-360-1500}
  \caption{Total protein fluctuation in the right, middle, and left
    parts of a equilateral (top), iscoscolese (middle), and 3-4-5
    (bottom) triangle.  The vertical axis shows stacked the total
    number of proteins that are of four different compound stages and
    in the different sections of the cell.}
  \label{box-triangle}
\end{figure}

The double pole oscillation pattern, where one pole is located in a
single corner of the triangle and the other pole is spread out between
the opposite two, can be seen in Figure \ref{box-triangle}.  The
equilateral triangle shows a spike in both the Center and Left
sections at the same time, both showing the familiar sequence of peaks
amoungst the different states of the protein seen in the poles of the
pill shaped bacteria.  A spike in the other corner, showing the common
sequence, occurs during the minima of the former two, wth a higher
concentration at the peak.  A similar pattern is seen in the
iscosolese triangular shape, where interestingly the onset of the
maxima in the single maxima corner (the Left section) builds more
quickly than it fades.  This is presumably becuase as the cytoplasmic
minD:ATP diffuses down a more accute corner, it is sourrounded by
closer cell walls than it would be in a less acute corner, so that the
it is more apt at any diffusive step to make contact and cluster on
the walls.  That particular part of the process is therefore
accelerated, driving the build up of the maxima forward.  The right
triangle shows a similar pattern.

@@

>>>>

\subsection{Triangular Shapes}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-400-400-400-1500}
  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-500-300-500-1500}
  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-480-360-1500}
  \caption{Total protein fluctuation in the right, middle, and left
    parts of an equilateral (top), iscoscolese (middle), and 3-4-5
    (bottom) triangle.  The vertical axis shows stacked the total
    number of proteins that are of four different compound stages and
    in the different sections of the cell.}
  \label{box-triangle}
\end{figure}

The double pole oscillation pattern, in which one pole is located in a
single corner of the triangle and the other pole is spread out between
the opposite two, can be seen in Figure \ref{box-triangle}.  The
equilateral triangle shows a spike in both the Center and Left
sections at the same time, both showing the familiar sequence of peaks
amoungst the different states of the protein seen in the poles of the
pill shaped bacteria.  A spike in the other corner, showing the common
sequence, occurs during the minima of the former two, wth a higher
concentration at the peak.  A similar pattern is seen in the
iscosolese triangular shape, where interestingly the onset of the
maxima in the single maxima corner (the Left section) builds more
quickly than it fades.  This is presumably becuase as the cytoplasmic
minD:ATP diffuses down a more accute corner, it is sourrounded by
closer cell walls than it would be in a less acute corner, so that the
it is more apt at any diffusive step to make contact and cluster on
the walls.  That particular part of the process is therefore
accelerated, driving the build up of the maxima forward.

The right triangle shows a similar pattern except that here there is
an assymetry between the two corners that maximize at roughly the same
time.  One corner is further from the single maximizing corner and it
consisitently peaks later.  The MinD simply have further to travel
before they maximize there.

For these three sizess and shapes there is not sign that the
oscillation patterns once they are set will break down.

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-601-601-601-1500}
  \caption{Total protein fluctuation of an equilateral triangle with
    larger dimensions (each side is roughly $6\mu m$.  The vertical
    axis shows stacked the total number of proteins that are of four
    different compound stages and in the different sections of the
    cell. The time limits have been set to show the broken down
    section of the simulation.}
  \label{box-triangle}

The larger equilateral shape shows the same pattern as the smaller
version does only until fifteen periods, at which point there is a
breakdown of the oscillation pattern.  During the last three stable
periods, the single maximizing corner, the lower left section in the
figure, has a lower peak each period as the membrane bound MinD:ATP in
the other corners lag more and more before being eaten away by the
MinE.  Finally these maxima lag so much that they break down the
regular pattern.  There then occurs about five periods of semi chaotic
behavoir, until it settles back into another stable oscillation that
is similar to the original one, except that a different corner has
been chosen to be the singlular maxima (the right section in the
figure), while the other two corners maximize at the same time.  This
interesting breakdown and recovery shows both the robustness of the
double pole oscilatory tendency and the importance of required
distance of travel for the different proteins.

\end{figure}

Fifteen

@@

Simulations of this shape that has the same height and dimensions .6
times the size do not exhibit the same pattern.  In these the MinD
maxima oscillate quickly back and forth between the two lower corner
poles.

Simulations in which the two planar dimensions are 2 and then 3 times
the size (cells roughly $6\mu m$ and $9\mu m$, respectively, from top
to bottom) show no stable regular periodic pattern \fixme{although
  they haven't really run long enough to exhibit much.  They certainly
  won't show the double oscillation pattern, however.}  The animations
of $6\mu m$ cells show that the MinD acts as a sort of traveling
cluster that is constantly being eaten away be MinE behind it.  When
this cluster enters a region of high curvature that ends in a dead end
corner it performs the polar maxima behavoir seen in the other
simulations, regrouping out away from the corner where it travels in
the opposite direction while being ``chased'' away by the MinE that
has itself maximized in the corner.  If it has just maximized in the
top corner, it regroups traveling downward and then naturally splits
into two groups that travel out and form maxima in the two opposite
bottom corners.  After maximizing in these two corners the two groups
recombine again in the center and travel in some direction together as
one cluster.  Simulations of the $9\mu m$ cells show a similar roaming
cluster.  Although here, the maxima occur on non-polar walls often,
and will often split into two roaming clusters that interact less
quickly and are less correlated than those seen in the $6\mu m$ cell.

It seems that there is an approximate critical cell size for which the
MinD will act in these ``wandering cluster'' formations.  The cell is
large enough so that there is a loss of MinD correlation between the
opposite sides (the protein in the right corner at any time is too far
away from the left to immediately affect the protein there).
